\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage[a4paper, margin=2cm]{geometry} % Minskade marginalen något för att få mer plats

\title{Requirements Specification - LTU Search Engine}
\author{Fullstack Developer .NET}
\date{\today}

\begin{document}

\maketitle

\section{Functional Requirements}

\renewcommand{\arraystretch}{1.5}

% Kolumnbredder: ID (2.2cm), Beskrivning (9cm), Test (4.5cm)
\begin{longtable}{@{}p{1.7cm} p{9cm} p{4.5cm}@{}}
\caption{Functional Requirements List}\\
\toprule
\textbf{RQ ID} & \textbf{Description} & \textbf{Test Method} \\
\midrule
\endfirsthead

\multicolumn{3}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\textbf{RQ ID} & \textbf{Description} & \textbf{Test Method} \\
\midrule
\endhead

\midrule
\multicolumn{3}{r}{{Continued on next page}} \\
\bottomrule
\endfoot

\bottomrule
\endlastfoot

% --- CRAWLER (1xxx) ---
\multicolumn{3}{l}{\textbf{\textit{Crawler (1000 Series)}}} \\
\midrule
FRQ-1001 & The system shall crawl web pages starting from a given seed URL. &  Test Crawl starts from provided seed URL \\
FRQ-1002 & The system shall follow internal links recursively. & \\
FRQ-1003 & The system shall limit crawling speed max 300 requestsminute (limit the site requests). & \\
FRQ-1004 & The crawler must parse and adhere to the ``robots.txt'' file of the target domain. & \\
FRQ-1005 & The system shall restrict crawling to a configurable whitelist of domains. & \\
FRQ-1006 & The crawler shall avoid crawling the same URL more than once per execution. & \\
FRQ-1007 & The crawler shall ignore non-relevant resources (images, CSS, JS). & \\
FRQ-1008 & The crawler must only search within the domain specified in the whitelist. & \\
FRQ-1009 & The system must support adding new domains to a whitelist automatically. & \\
FRQ-1010 & The crawler must detect linked PDF files and include them in the index. & \\
FRQ-1011 & The crawler must not follow/crawl links found inside PDF documents. & \\

% --- INDEXING (2xxx) ---
\midrule
\multicolumn{3}{l}{\textbf{\textit{Indexing (2000 Series)}}} \\
\midrule
FRQ-2001 & The system shall extract textual content from HTML pages. & \\
FRQ-2002 & The system shall store indexed terms together with page references (inverted index). & \\
FRQ-2003 & The system shall support incremental updates of the index. & \\
FRQ-2004 & The system shall ignore non-textual content (images, videos, binaries). & \\


% --- SEARCHING (3xxx) ---
\midrule
\multicolumn{3}{l}{\textbf{\textit{Searching (3000 Series)}}} \\
\midrule
FRQ-3001 & A query must be able to match characters strictly if no other option is chosen. & \\
FRQ-3002 & A query must be able to match more then one set of characters, if the option (AND) to do so is chosen. & \\
FRQ-3003 & The query shall support optional characters using the OR operator. 
            Example: If the query searches for "cat OR dog", results must 
            include items containing either "cat" or "dog".                         & \\
FRQ-3004 & Use same syntax as other providers (standard search syntax). & \\
FRQ-3005 & Results of queries must be paginated when more than 10 results are found. & \\
FRQ-3006 & The results should contain the headline of the context found. & \\
FRQ-3007 & The results should contain a snippet with keywords highlighted. & \\
FRQ-3008 & Search results must be ranked by relevance. & \\
FRQ-3009 & The system shall provide a search API for the UI. & \\

% --- USER INTERFACE (4xxx) ---
\midrule
\multicolumn{3}{l}{\textbf{\textit{User Interface (4000 Series)}}} \\
\midrule
FRQ-4001 & The system shall provide a web-based search interface. & \\
FRQ-4002 & The system shall allow users to enter search queries and view results. & \\
FRQ-4003 & The UI shall indicate the current page (pagination state). & \\
FRQ-4004 & The UI shall display a clear message when no results are found. & \\

\end{longtable}

\section{Low-Priority Functional Requirements}
\begin{longtable}{@{}p{2.2cm} p{9cm} p{4.5cm}@{}}
\toprule
\textbf{RQ ID} & \textbf{Description} & \textbf{Test Method} \\
\midrule
L-FRQ-5001 & The query should be able to handle wildcards. & \\
L-FRQ-5002 & An estimation of the completed query should be suggested (Autocomplete). & \\
\bottomrule
\end{longtable}

\section{Non-Functional Requirements}
\begin{longtable}{@{}p{2.2cm} p{9cm} p{4.5cm}@{}}
\toprule
\textbf{RQ ID} & \textbf{Description} & \textbf{Test Method} \\
\midrule
NFRQ-6001 & A query should take no longer than 10 seconds. & \\
NFRQ-6002 & The search engine should search the whole LTU-Domain (with exceptions). & \\
NFRQ-6003 & The system shall only index publicly available HTML pages. & \\
\bottomrule
\end{longtable}

% Non-Testable RQ 
\section{Non-Testable RQ}
\begin{itemize}
  \item FRQ-2005 The system shall use a clearly defined data structure (e.g., ER diagram).
  \item FRQ-3001 A query containing 2-3 words should return the correct result.
\end{itemize}


\end{document}
